The speed of PyPy

### 2009-11-05 talk/rupy2009/talk.tex
update

\begin{frame}
  \frametitle{Nomenclature}
  \begin{itemize}
    \item Python - a programming language
    \item CPython - main implementation of Python
      xxx
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{More about this example}
  \begin{tabular}{| l | c | c | c | c |}
    \hline
    & CPython & JVM & Psyco & PyPy \\
    Average of 10 runs & 7.6s & 0.77s & 4.4s & 1.3s \\
    \hline
  \end{tabular}
  \vspace{.5cm}
  \pause
  \begin{itemize}
    \item So, it's CPython that is slow on this particular benchmark
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Nomenclature}
  \begin{itemize}
    \item Python - a programming language
    \item CPython - main implementation of Python
    \item JVM - Java Virtual Machine - VM used to run Java, among others
    \item JIT - Just in time compiler
    \item Psyco - JIT for Python
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{More about this example}
  \begin{tabular}{| l | c | c | c | c |}
    \hline
    & CPython & JVM & Psyco & PyPy \\
    Average of 10 runs & 7.6s & 0.77s & 4.4s & 1.3s \\
    \hline
  \end{tabular}
  \vspace{.5cm}
  \pause
  \begin{itemize}
    \item So, it's CPython that is slow on this particular benchmark
      \pause
    \item Same example, using numpy and vectorization about 3x faster than JVM
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Python's speed}
  \begin{itemize}
    \item Instead of: ``Why is Python slow?''
      \pause
    \item Better: ``Why is Python hard to optimize?''
      \pause
    \item Even better: ``How are we going to fix it?''
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Why is Python hard to optimize?}
  \begin{itemize}
    \item Duck typing (dynamic dispatch)
    \item Frames
    \item Object encapsulation
    \item Dictionaries of instances
  \end{itemize}
\end{frame}

\begin{frame}
\end{frame}
